### 2023-02-13 article.tex
Online paper has more figures

This paper has been produced following all recommendations in it:
it's \LaTeX code is hosted on GitHub 
at \url{https://github.com/richelbilderbeek/chapter_paradata}.
Due this, one can, among others, see the complete version history of this paper.
This alone could allow research to be done on, for example,
the effect of reviewers' feedback on a first manuscript.

>>>>

This book chapter has been produced following all recommendations in it:
it's \LaTeX code is hosted on GitHub 
at \url{https://github.com/richelbilderbeek/chapter_paradata}.
Due this, one can, among others, see the complete version history of this paper.
This alone could allow research to be done on, for example,
the effect of reviewers' feedback on a first manuscript.
The website also supplies an alternative version of the same chapter
with more figures.
